---
title: "Draft_Mid_Term"
author: "Yiping Ying"
date: "2022-09-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# II.Data Manipulation and Visualization

## 2.0 Set Up
```{r load_packages, include=FALSE}

# You can set some global options for knitting chunks

knitr::opts_chunk$set(echo = TRUE)

# Load some libraries

library(tidyverse)
library(sf)
library(spdep)
library(caret)
library(ckanr)
library(FNN)
library(grid)
library(gridExtra)
library(ggcorrplot) # plot correlation plot
library(corrr)      # another way to plot correlation plot
library(kableExtra)
library(jtools)     # for regression model plots
library(ggstance) # to support jtools plots
library(ggpubr)    # plotting R^2 value on ggplot point scatter
library(broom.mixed) # needed for effects plots
library(stargazer)
library(tidycensus)

options(scipen = 999)
options(tigris_class = "sf")

# functions and data directory

source("https://raw.githubusercontent.com/urbanSpatial/Public-Policy-Analytics-Landing/master/functions.r")

palette5 <- c("#0571b0","#92c5de","#ffffbf","#f4a582","#ca0020")

setwd("~/Github/508_houseprice_prediction")
```

```{r load_key, warning = FALSE,message=FALSE}
census_api_key("c1c749a5ad57fa58fe19e1403d894e9acef41a97", install=TRUE,overwrite = TRUE)
```
## 2.1 Data Wrangling

### 2.1.1 Data loading
```{r raw_data}
#Raw Data:
data<-st_read("~/Github/508_houseprice_prediction/data/studentData.geojson")

#Add age,pricepersq,bathrooms
data<-data %>% mutate(AGE = 2022-yearbuilt,
                                pricepersq = price/shape_Area,
                                bathrooms = fullbaths+halfbaths)
```

```{r download_data,warning=FALSE,message=FALSE}
#download open data,crs=4326(?ESRI:103500)

#Census Tract:
tract<-st_read('~/Github/508_houseprice_prediction/data/CensusTract/Census_Tracts_2020.shp')
tract<-tract %>% st_transform(crs=4326)

#Zipcode:
##用于neighborhood effects分析
zipcode<-st_read('~/Github/508_houseprice_prediction/data/zipcode/Zipcode.shp')
zipcode<-zipcode %>% st_transform(crs=4326) %>% rename(shapeLeng = shape_Leng,shapeArea = shape_Area) %>% dplyr::select(zip,po_name,shapeLeng,shapeArea)
```

```{r amenity_facility_feature,warning=FALSE}
#1.college:
college<-st_read('./data/college/Colleges.shp')
college.sf<-college %>% st_transform(crs = 4326) %>% dplyr::select(geometry) %>% na.omit() 
#2.daycare:
daycare<-st_read('./data/daycare/Daycare.shp')
daycare.sf<-daycare %>% st_transform(crs=4326)%>% dplyr::select(geometry) %>% na.omit() 

#3.Medical Facilities:
MedicalFacilities<-st_read('./data/medical/MedicalFacilities.shp')
MedicalFacilities.sf<-MedicalFacilities %>% st_transform(crs=4326)%>% dplyr::select(geometry) %>% na.omit()

#4.library:
## 数目不太多
library<-st_read('./data/library/Library.shp')
library.sf<-library %>% st_transform(crs=4326)%>% dplyr::select(geometry) %>% na.omit() 

#5.Historical cemeteries:
## 原始数据是polygon,为了方便计算，使用st_centroid取了每个polygon的质心
hist_cemeteries<-st_read('./data/historic_cemeteries/Historic_Cemeteries.shp')
hist_cemeteries.sf<-hist_cemeteries %>% st_transform(crs=4326)%>% st_centroid() %>% dplyr::select(geometry) %>% na.omit() 

#6.Historical Properties:
## 原始数据是polygon,为了方便计算，使用st_centroid取了每个polygon的质心
hist_properties<-st_read('./data/historic_properties/HistoricProperty_National.shp')
hist_properties.sf<-hist_properties%>% st_transform(crs=4326)%>%st_centroid() %>% dplyr::select(geometry) %>% na.omit() 

#7.church
## 数目非常多
church<-st_read('./data/church/Churches.shp')
church.sf<-church %>% st_transform(crs=4326)%>% dplyr::select(geometry) %>% na.omit() 

#8.park_amenities:
park_amenities<-st_read('./data/park_amenities/ParkAmenity.shp')
park_amenities.sf<-park_amenities%>% st_transform(crs=4326)%>% dplyr::select(geometry) %>% na.omit() 

#9.park easement:
park_easement<-st_read('./data/park_easement/ParkEasements.shp')
park_easement.sf<-park_easement%>% st_transform(crs=4326)%>%st_centroid() %>% dplyr::select(geometry) %>% na.omit()

#10.park location:
park_location <- st_read('./data/Park_Locations/Park_Locations.shp')
park_location.sf <- park_location %>% st_transform(crs=4326)%>%st_centroid() %>% dplyr::select(geometry) %>% na.omit()


#11.Capital Improvement Projects:
capital_improve<-st_read('./data/Capital_Improvement_Projects/Capital_Improvement_Projects.shp')
capital_improve.sf<-capital_improve %>% st_transform(crs=4326)%>% dplyr::select(geometry) %>% na.omit() 

#12.Business Investment Opportunity Zones:
##这个=做binary指标。原始数据是polygon;考虑使用buffer?
business_invest<-st_read('./data/Business/Business_Investment_Opportunity_Zones.shp')
business_invest<-business_invest %>% st_transform(crs=4326)
```

```{r}
ggplot()+
  geom_sf(data=st_union(zipcode))+
  geom_sf(data=business_invest)
```

```{r}
business_invest_union<-business_invest %>% st_union() %>% st_sf()

isin<-st_within(data,business_invest_union) %>% lengths>0

isin<-data.frame(isin)

data<-cbind(data,isin)
```


```{r}
ggplot()+
  geom_sf(data=st_union(tract))+
  geom_sf(data=park_easement.sf)
```

```{r neighborhood_effects_factor_and_clean}
#spatial features collection
##这个chunk内的都是以census tract为单位的指标；将合并到data

#1.Crime:
crime<-st_read('./data/Crime - Violent.geojson')
crime<-crime %>% st_transform(crs=4326)
crime1<-crime %>% mutate(crime_sum = X2019.raw+X2020.raw+X2021.raw) %>%  dplyr::select(crime_sum) 

#2.Long Commute:
long_commute<-st_read('./data/LongCommute.geojson')
long_commute<-long_commute %>% st_transform(crs=4326) %>% mutate(PctLongCommute = X2020) %>%  dplyr::select(PctLongCommute)

#3.Percent of Grocery:
grocery<-st_read('./data/Proximity to a Grocery Store.geojson')
Pctgrocery<-grocery %>% st_transform(crs=4326) %>% mutate(Pctgrocery = X2021) %>%  dplyr::select(Pctgrocery)

#4.Percent of Test Proficiency in Elementary Schools:
test_elementary<-st_read('./data/Test Proficiency - Elementary School.geojson')
Pcttest1<-test_elementary%>% st_transform(crs=4326) %>%mutate( test.elementary = X2019) %>% dplyr::select(test.elementary)

#5.Percent of Test Proficiency in Middle Schools:
test_middle<-st_read('./data/Test Proficiency - Middle School.geojson')
Pcttest2<-test_middle%>% st_transform(crs=4326) %>%mutate( test.middle = X2019) %>% dplyr::select(test.middle)

#6.Percent of Test Proficiency in High Schools:
test_high<-st_read('./data/Test Proficiency - High School.geojson')
Pcttest3<-test_high%>% st_transform(crs=4326) %>% mutate(test.high = X2019) %>% dplyr::select(test.high)

#7.Percent of Bachelor's Degree:
bachelor<-st_read('./data/Education Level - Bachelor Degree.geojson')
PctBachelor<-bachelor %>% st_transform(crs=4326) %>% mutate(PctBachelor = X2020) %>% dplyr::select(PctBachelor)

#8.Median Age of Residents:
age<-st_read('./data/Age of Residents.geojson')
MedAge<-age %>% st_transform(crs=4326) %>% mutate(MedAge = X2020) %>% dplyr::select(MedAge)
```

Census Data:
```{r census_data,include=FALSE}
options(tigris_use_cache = TRUE)

acs_variable_list.2020 <- load_variables(2020, 
                                         "acs5", 
                                         cache = TRUE)

tracts20 <- 
  get_acs(geography = "tract", variables = c("B25026_001E","B02001_002E", "B19013_001E","B25058_001E","B06012_002E",                            
"B25002_003E","B25004_002E","B25004_003E","B25004_004E","B25004_005E",
"B25001_001E","B08137_003E"), 
          year=2020, state= 37, county= 119, geometry=T, output="wide")%>% st_transform(crs=4326) %>%
  rename(TotalPop = B25026_001E, 
         Whites = B02001_002E,
         MedHHInc = B19013_001E, 
         MedRent = B25058_001E,
         TotalPoverty = B06012_002E,
         TotalVacant = B25002_003E,
         ForRent = B25004_002E,
         ForRentVac = B25004_003E,
         ForSale = B25004_004E,
         ForSaleVac = B25004_005E,
         TotalUnit = B25001_001E,
         RenterOccupied = B08137_003E
         ) %>%
  dplyr::select(-NAME, -starts_with("B")) %>% #-starts_with("B") awesome!
  mutate(pctWhite = ifelse(TotalPop > 0, Whites / TotalPop,0),
         pctPoverty = ifelse(TotalPop > 0, TotalPoverty / TotalPop, 0),
         pctTotalVacant = ifelse(TotalUnit > 0, TotalVacant / TotalUnit * 100, 0),
         TotalOccupied = TotalUnit - TotalVacant,
         pctRenterOccupied = ifelse(TotalOccupied >0, RenterOccupied/TotalOccupied, 0)) %>%
  dplyr::select(-Whites, -TotalPoverty) 
```

### 2.1.2 Feature Engineering

```{r}
ggplot()+
  geom_sf(data=zipcode)
```

```{r data_left_join}
data<-st_join(data,crime1)
data<-st_join(data,long_commute)
data<-st_join(data,Pctgrocery)
data<-st_join(data,Pcttest1)
data<-st_join(data,Pcttest2)
data<-st_join(data,Pcttest3)
data<-st_join(data,PctBachelor)
data<-st_join(data,MedAge)
data<-st_join(data,zipcode)
data<-st_join(data,tracts20)
```

```{r knn}
st_c<-st_coordinates

#1.college:
data <-
  data %>% 
  mutate(
    college_nn1 = nn_function(st_c(data),st_c(college.sf), 1),
    college_nn2 = nn_function(st_c(data),st_c(college.sf), 2),
    college_nn3 = nn_function(st_c(data),st_c(college.sf), 3),
    college_nn4 = nn_function(st_c(data),st_c(college.sf), 4),
    college_nn5 = nn_function(st_c(data),st_c(college.sf), 5),
    ) 

#2.daycare:
data <-
  data %>% 
  mutate(
    daycare_nn1 = nn_function(st_c(data),st_c(daycare.sf), 1),
    daycare_nn2 = nn_function(st_c(data),st_c(daycare.sf), 2),
    daycare_nn3 = nn_function(st_c(data),st_c(daycare.sf), 3),
    daycare_nn4 = nn_function(st_c(data),st_c(daycare.sf), 4),
    daycare_nn5 = nn_function(st_c(data),st_c(daycare.sf), 5),
    )

#3.Medical Facilities:
data <-
  data %>% 
  mutate(
    MedicalFacilities_nn1 = nn_function(st_c(data),st_c(MedicalFacilities.sf), 1),
    MedicalFacilities_nn2 = nn_function(st_c(data),st_c(MedicalFacilities.sf), 2),
    MedicalFacilities_nn3 = nn_function(st_c(data),st_c(MedicalFacilities.sf), 3),
    MedicalFacilities_nn4 = nn_function(st_c(data),st_c(MedicalFacilities.sf), 4),
    MedicalFacilities_nn5 = nn_function(st_c(data),st_c(MedicalFacilities.sf), 5),
    )

#4.library:
data <-
  data %>% 
  mutate(
    library_nn1 = nn_function(st_c(data),st_c(library.sf), 1),
    library_nn2 = nn_function(st_c(data),st_c(library.sf), 2),
    library_nn3 = nn_function(st_c(data),st_c(library.sf), 3),
    library_nn4 = nn_function(st_c(data),st_c(library.sf), 4),
    library_nn5 = nn_function(st_c(data),st_c(library.sf), 5),
    )

#5.Historical cemeteries:
data <-
  data %>% 
  mutate(
    hist_cemeteries_nn1 = nn_function(st_c(data),st_c(hist_cemeteries.sf), 1),
    hist_cemeteries_nn2 = nn_function(st_c(data),st_c(hist_cemeteries.sf), 2),
    hist_cemeteries_nn3 = nn_function(st_c(data),st_c(hist_cemeteries.sf), 3),
    hist_cemeteries_nn4 = nn_function(st_c(data),st_c(hist_cemeteries.sf), 4),
    hist_cemeteries_nn5 = nn_function(st_c(data),st_c(hist_cemeteries.sf), 5),
    )

#6.Historical Properties:
data <-
  data %>% 
  mutate(
    hist_properties_nn1 = nn_function(st_c(data),st_c(hist_properties.sf), 1),
    hist_properties_nn2 = nn_function(st_c(data),st_c(hist_properties.sf), 2),
    hist_properties_nn3 = nn_function(st_c(data),st_c(hist_properties.sf), 3),
    hist_properties_nn4 = nn_function(st_c(data),st_c(hist_properties.sf), 4),
    hist_properties_nn5 = nn_function(st_c(data),st_c(hist_properties.sf), 5),
    )

#7.church
data <-
  data %>% 
  mutate(
    church_nn1 = nn_function(st_c(data),st_c(church.sf), 1),
    church_nn2 = nn_function(st_c(data),st_c(church.sf), 2),
    church_nn3 = nn_function(st_c(data),st_c(church.sf), 3),
    church_nn4 = nn_function(st_c(data),st_c(church.sf), 4),
    church_nn5 = nn_function(st_c(data),st_c(church.sf), 5),
    )

#9.park easement:
data <-
  data %>% 
  mutate(
    park_location_nn1 = nn_function(st_c(data),st_c(park_location.sf), 1),
    park_location_nn2 = nn_function(st_c(data),st_c(park_location.sf), 2),
    park_location_nn3 = nn_function(st_c(data),st_c(park_location.sf), 3),
    park_location_nn4 = nn_function(st_c(data),st_c(park_location.sf), 4),
    park_location_nn5 = nn_function(st_c(data),st_c(park_location.sf), 5),
    )

#10.Capital Improvement Projects:
data <-
  data %>% 
  mutate(
    capital_improve_nn1 = nn_function(st_c(data),st_c(capital_improve.sf), 1),
    capital_improve_nn2 = nn_function(st_c(data),st_c(capital_improve.sf), 2),
    capital_improve_nn3 = nn_function(st_c(data),st_c(capital_improve.sf), 3),
    capital_improve_nn4 = nn_function(st_c(data),st_c(capital_improve.sf), 4),
    capital_improve_nn5 = nn_function(st_c(data),st_c(capital_improve.sf), 5),
    )
```



### 2.1.3 Split dataset
```{r challenge_set}
#challenge_set:用于最后预测的组，crs=4326
challenge_set<-data %>% filter(price==0)
```

```{r model_set}
#model_set:建模组,crs=4326
model_set<-data %>% filter(price!=0)
```
## 2.2 Summary Statistics of Features

model_set internal features
```{r summary_internal_features}
#Summary and selection of internal features:
internal.variable <- c("price",
                "shape_Area",
                "pricepersq",
                "AGE",
                "heatedarea",
                "numfirepla",
                "fullbaths",
                "halfbaths",
                "bedrooms",
                "units")

internal.features<-model_set[internal.variable] %>%
  st_drop_geometry()


#stargazer:
stargazer(internal.features, type = "html", 
          title = "Table DATA 2.1 Summary Statistics of Internal Characteristics ",
          header = FALSE,
          single.row = TRUE)
```

```{r internal_feature_correlation_matrix}
#Correlation matrix of internal features:
numericVars <- 
  select_if(internal.features, is.numeric) %>% na.omit()

ggcorrplot(
  round(cor(numericVars), 1), 
  p.mat = cor_pmat(numericVars),
  colors = c("#0571b0", "#ffffff", "#ca0020"),
  type="lower",
  insig = "pch") +  
    labs(title = "Correlation across numeric variables\n(internal features)\n")+plotTheme()
```
remove AGE, units is a good feature do not have strong correlation with other features and have strong corelation with price.
```{r}
sel.internal.list <-  c("price",
                "shape_Area",
                "heatedarea",
                "numfirepla",
                "fullbaths",
                "halfbaths",
                "bedrooms",
                "units")
```


```{r summary_amenities_feature}
amenities_feature.list<-model_set %>% dplyr::select(
  starts_with('college_'),
  starts_with('daycare_'),
  starts_with('MedicalFacilities_'),
  starts_with('library_'),
  starts_with('hist_'),
  starts_with('church'),
  starts_with('park_'),
  starts_with('capital_'),
  price) %>% 
  st_drop_geometry()

#stargazer:
stargazer(amenities_feature.list, type = "html", 
          title = "Table DATA 2.1 Summary Statistics of Internal Characteristics ",
          header = FALSE,
          single.row = TRUE)
```

```{r amenities_feature_matrix}
ggcorrplot(
  round(cor(amenities_feature.list), 1), 
  p.mat = cor_pmat(amenities_feature.list),
  colors = c("#0571b0", "#ffffff", "#ca0020"),
  type="lower",
  insig = "pch") +  
  labs(title = "Correlation across numeric variables\n(amenity features)\n")+plotTheme()+
  theme(axis.title.x = element_text(size=3),axis.title.y = element_text(size=3))
```

```{r}
#Amenities
sel.amenitie<-model_set%>% dplyr::select(
  starts_with('college_'),
  starts_with('daycare_'),
  starts_with('MedicalFacilities_'),
  starts_with('library_'),
  starts_with('hist_'),
  starts_with('church'),
  starts_with('capital_'),
  price) %>% 
  st_drop_geometry()
```

```{r}
#Tract Feature
tract.list <- c("pctTotalVacant", "pctRenterOccupied", "pctWhite","pctPoverty","MedRent" ,"MedHHInc","MedAge","crime_sum", "PctLongCommute", "Pctgrocery", "test.elementary","test.middle", "test.high","PctBachelor","MedAge",'price')

tract_feature.list<-model_set[tract.list]%>% 
  st_drop_geometry()

```

```{r amenities_feature_matrix}
numeric.tract<- 
  select_if(tract_feature.list, is.numeric) %>% na.omit()

ggcorrplot(
  round(cor(numeric.tract), 1), 
  p.mat = cor_pmat(numeric.tract),
  colors = c("#0571b0", "#ffffff", "#ca0020"),
  type="lower",
  insig = "pch") +  
  labs(title = "Correlation across numeric variables\n public service features\n")+plotTheme()+
  theme(axis.title.x = element_text(size=3),axis.title.y = element_text(size=3))


sel.tract.list<- c( "pctRenterOccupied", "pctWhite","pctPoverty","MedRent" ,"MedHHInc","MedAge","crime_sum", "PctLongCommute", "Pctgrocery",  "test.elementary","PctBachelor","MedAge",'price')
```

```{r histogram_train_feature}
model_set %>% 
  st_drop_geometry() %>% 
  dplyr::select(price,extwall,storyheigh,heatedfuel,aheatingty,bldggrade) %>%
   filter(price <= 5000000) %>%
  gather(Variable, Value, -price) %>% 
   ggplot(aes(Value, price)) +
     geom_bar(position = "dodge", stat = "summary", fun = mean) +
     facet_wrap(~Variable, ncol = 3, scales = "free") +
     labs(title = "Price as a function of\ncategorical variables", y = "Mean_Price") +
     theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r feature_enginneering_nonnumeric}
# 1.Modify extwall:
extwall.stone<-c("STONE")
data <- 
  data %>%
  mutate(extwall.m = ifelse(extwall %in% extwall.stone,"STONE","Non-STONE"))

# 2.Modify Aheatingty:
hotwater<-c("HOT WATER")
data<-data %>% mutate(aheatingty.m = ifelse(aheatingty %in% hotwater,"HOT WATER","ELSE" ))

# 3.Modify heatedfuel:
gas<-c("GAS")
data<-data %>% mutate(heatedfuel.m = ifelse(heatedfuel %in% gas,"GAS","ELSE" ))

# 4.Modify bldggrade
fairplus<-c("FAIR","MINIMUM","NA")
data<-data %>% mutate(bldggrade.m = ifelse(bldggrade %in% fairplus,"ELSE",bldggrade))

# 5.Modify storyheigh
storyelse<-c("NA","SPLIT LEVEL","BI-LEVEL","CAPE COD","RANCH W/BSMT")
data<-data %>% mutate(storyheigh.m = ifelse(storyheigh %in% storyelse,"ELSE",storyheigh ))
```



## 2.3 Regression for Feature Selection
### 2.3.1 non numeric Feature Selection

```{r}
outlier<-data %>% filter(price>2200000)
```

```{r}
ggplot()+
  geom_sf(data=st_union(tract))+
  geom_sf(data=outlier)
```

```{r challenge_set}
#challenge_set:用于最后预测的组，crs=4326
challenge_set<-data %>% filter(price==0)
```

```{r model_set}
#model_set:建模组,crs=4326
model_set<-data %>% filter(price!=0)
```


```{r}
numeric<- select_if(data, is.numeric)%>% na.omit()%>% 
  st_drop_geometry()
```
!(data %in% c(value1, value2, value3, ...))

```{r}
nonnumeric <- select_if(data, !(colnames(data)%in% colnames(numeric)))
```

```{r}
names(nonnumeric)
```

```{r,eval=FALSE}
#删除不再使用的数据集合
#a = ls()
#rm(list=a[which(a!='data' & a !='sel.internal.list' & a !='sel.tract.list' & a !='sel.amenitie' & a!='challenge_set'& a!= 'model_set')])
```

```{r}
#非数字的列
nonnumeric.feature1 <- c("descbuildi", "storyheigh.m", "aheatingty.m", "heatedfuel.m", "extwall.m", "foundation", "bldggrade.m","isin","price")
```
"stname", "sttype",  "city", "state",  

## 4.1 Dataset Splitting and Model Building

```{r model_set_split,warning=FALSE}
#1.Split Model Set:
set.seed(7278)

# get index for training sample:
inTrain<-caret::createDataPartition(
  y = paste(model_set$storyheigh,model_set$extwall,model_set$bldggrade,model_set$price),
  p = .60, 
  list=FALSE)

# split model_set into train and test
model_set.train<-model_set[inTrain,] %>% filter(price<=2200000)
model_set.test<-model_set[-inTrain,]
```

```{r}
#non-numeric feature
nonnumeric <- model_set.train %>% dplyr::select(nonnumeric.feature1)%>% 
  st_drop_geometry()
```

```{r M1_nonnumeric}
#第一个lm:回归非数字类型的列
M1 <- lm(price ~ ., data = nonnumeric)

summary(M1)
```

```{r M2_internal_feature}
# internal feature
sel.internal<-model_set.train %>% dplyr::select(sel.internal.list) %>% st_drop_geometry()
M2 <- lm(price ~ ., data = sel.internal)

summary(M2)
```

```{r M3_tract_feature}
sel.tract<-model_set.train %>% dplyr::select(sel.tract.list) %>% st_drop_geometry()
M3 <- lm(price ~ ., data = sel.tract)

summary(M3)
```

```{r }
sel.amenitie1<-model_set.train%>% dplyr::select(
  starts_with('college_'),
  starts_with('daycare_'),
  starts_with('MedicalFacilities_'),
  starts_with('library_'),
  starts_with('hist_'),
  starts_with('church'),
  starts_with('capital_'),
  price) %>% 
  st_drop_geometry()

M4 <- lm(price ~., data = sel.amenitie1)

summary(M4)
```

```{r}
train_set.1<-model_set.train %>% dplyr::select(
  price,
  #Non-numeric Feature
  descbuildi,bldggrade,
  #Internal Feature
  shape_Area , heatedarea , numfirepla , halfbaths , fullbaths , bedrooms , units,
  #Tract Feature
  pctRenterOccupied , pctWhite , pctPoverty , MedRent , MedHHInc , PctLongCommute, Pctgrocery, PctBachelor, test.high,
  #Amenities Feature
  college_nn2, daycare_nn5,MedicalFacilities_nn5,library_nn5,hist_cemeteries_nn1,hist_properties_nn4, hist_properties_nn5,capital_improve_nn2,capital_improve_nn3,capital_improve_nn4,capital_improve_nn5) %>% st_drop_geometry()

M5 <- lm(price ~ ., data = train_set.1)

summary(M5)
```

```{r backup}
train_set.2<-model_set.train %>% dplyr::select(
  price,
  #Non-numeric Feature
  bldggrade.m,storyheigh.m,foundation,
  #Internal Feature
  shape_Area ,heatedarea, numfirepla,fullbaths,halfbaths, bedrooms , units,
  #Tract Feature
  pctRenterOccupied , pctWhite ,pctPoverty,MedHHInc ,test.elementary,PctBachelor,crime_sum,PctLongCommute,Pctgrocery,
  #Amenities Feature
  college_nn5,daycare_nn1,MedicalFacilities_nn4,MedicalFacilities_nn5,library_nn3,library_nn4,library_nn2,hist_properties_nn5,capital_improve_nn3,capital_improve_nn4,capital_improve_nn5) %>% st_drop_geometry()

M6 <- lm(price ~ ., data = train_set.2)

summary(M6)
```

```{r all_features}
train_set.lipu<-model_set.train %>% dplyr::select(price,
  nonnumeric.feature1,sel.internal.list,sel.tract.list,
  starts_with('college_'),
  starts_with('daycare_'),
  starts_with('MedicalFacilities_'),
  starts_with('library_'),
  starts_with('hist_'),
  starts_with('church'),
  starts_with('capital_')
) %>% st_drop_geometry()

M_0 <- lm(price ~ ., data = train_set.lipu)

summary(M_0)
```

## Map Home Price
```{r plot_home_price}
#Plot of home price per square feet:
ggplot()+
  geom_sf(data=zipcode,fill="grey40",color="white")+
  geom_sf(data=model_set,aes(color=q5(pricepersq)),show.legend="point",size=.75)+
  scale_color_manual(values = palette5,labels = qBr(model_set, "pricepersq"),name = "House Price\nPer Square Feet\n(Quintile Breaks)")+
  labs(title="House Price",subtitle = "Mecklenberg County,NC",caption="Figure1.1")+
  mapTheme()
```
